---
title: "IDACombo Analysis of Follow-Up Screen Results"
output: html_document
date: "2025-04-07"
---

This is part one of 2 scripts. This script generates the IDACombo scores for the drug screening data on the BRAF resistant cell line clones generated by the Raj lab. 

The second script - IDACombo_Graphs.Rmd - takes the output of this script and generates graphs. 

*NOTE, any data generated is not automatically saved. The lines to save them are commented out. 

#Setup 
Load Packages: 
```{r}
if (!requireNamespace("IDACombo", quietly = TRUE))
    devtools::install_github(repo = "https://github.com/Alexander-Ling/IDACombo/tree/master")

library(tidyverse)
library(IDACombo)
library(rgl)
library(car)
library(common)
set.seed(20250410)
```


# Format the Follow-Up Panel Screening Data

```{r}
# Read the dataset (adjust file path if necessary)
data <- read.delim("./Data/followup_panela_data.tsv", header = TRUE, sep = "\t")


#there are a number of values where the toxicity is negative, 
#this isn't readily interpretable and may mess with the IDACombo algorithm as it will expect the highest Viability to be 100, so I'm going to make a transformation for those values
# Previously our IDACombo analysis has just set the max and minimum to just be 0 and 1, but to maintain some of the trend, I'm going to just use a punitive transformation, which penalizes values outside this range 


# Define the punitive transformation
punitive_transform <- function(x, max_val, target_val) {
  if  (max_val > 0) {
  scale_factor <- log1p(max_val) / target_val  # Calculate scaling factor
  transform <- log1p(x) / scale_factor  }       # Apply scaled log transformation
  
  else if (max_val < 0) {
  scale_factor <- log1p(-max_val) / target_val  # Calculate scaling factor
  transform <- log1p(-x) / scale_factor  }      # Apply scaled log transformation
  
  return(transform)
}


# Apply the transformation only to positive values
original_tox <- data$Toxicity
max_negative <- min(original_tox, na.rm = TRUE)  # Find the most negative value
target_value <- -7                                # Define the target value for max

new_tox <- original_tox
new_tox[!is.na(new_tox) & new_tox < 0] <- #replace only the negative non-NA values
  punitive_transform(new_tox[!is.na(new_tox) & new_tox < 0], max_negative, target_value)

data$Viability <- 100 - new_tox

#The below code can be used to generate the same file that was used with the IDACombo Simplicity App
input_data <- data %>%
  group_by(Drug = Name, Cell_Line = CellLine, Drug_Dose = Dose) %>%
  summarize(Efficacy = mean(Viability),  Efficacy_SE = sd(Viability)/sqrt(2)) %>% #SE is sd/sqrt(n)
  ungroup() %>% 
  filter(Cell_Line != "Parental") #all of the analyses done are on the resistant cells only, so filtering those out


# input_data %>%
#   readr::write_tsv(file = "IDACombo_Input_noParental_v2.tsv")

```


Get all the drugs and all the possible drug combinations for IDACombo
```{r}
all_drugs <- unique(input_data$Drug)
table_all_drugs <- t(combn(x = all_drugs, m = 2))
```


# Calculate IDACombo Scores

For more information on IDACombo visit: 
https://oncotherapyinformatics.org/idacombo/
https://www.nature.com/articles/s41467-020-19563-6

This chunk gets the for loop started 
```{r}

#the settings can be found by looking at the links above
#importantly, Calcuate_Uncertainty is set to TRUE as this will enable p-value estimation for the IDACombo scores,
  #for this, the data needs to have the efficacy SE column

temp <- IDAPredict.2drug(Monotherapy_Data = as.data.frame(input_data), 
                 Cell_Line_Name_Column = "Cell_Line", 
                 Drug_Name_Column = "Drug", 
                 Drug_Concentration_Column = "Drug_Dose", 
                 Efficacy_Column = "Efficacy",
                 Efficacy_SE_Column = "Efficacy_SE",
                 LowerEfficacyIsBetterDrugEffect = TRUE, 
                 Efficacy_Metric_Name = "Viability",
                 Drug1 = table_all_drugs[1,1], 
                 Drug2 = table_all_drugs[1,2], 
                 Average_Duplicate_Records = FALSE, 
                 n_Simulations = 10000, 
                 Calculate_IDAcomboscore_And_Hazard_Ratio = TRUE, 
                 Calculate_Uncertainty = TRUE, 
                 Return_Bootstrap_Values = FALSE
                 ) 


All_IDACombo_Scores <- temp[[1]] %>% 
  mutate(Drug1 = all_drugs[1], Drug2 = all_drugs[2]) %>% 
  mutate(across(.cols = starts_with("p_"), 
                .fns =  function(column){as.numeric(gsub("<", "", column))}   )  ) #note, that several p-values are actually less what is listed

#the IDACombo package only provides exact values for values above 0.001, so any value below is just rounded to 0.001. 
#for this analysis, it doesn't matter as these values will still be called "significant" after BH multiple test correction
```


## for loop over all drugs

This chunk gets every drug combination IDACombo scores otuand  
```{r}
for(i in 2:nrow(table_all_drugs)) { 
  
  first_drug <- table_all_drugs[i,1]
  second_drug <- table_all_drugs[i,2]
  
temp <- IDAPredict.2drug(Monotherapy_Data = as.data.frame(input_data), 
                Cell_Line_Name_Column = "Cell_Line", 
                 Drug_Name_Column = "Drug", 
                 Drug_Concentration_Column = "Drug_Dose", 
                 Efficacy_Column = "Efficacy",
                 Efficacy_SE_Column = "Efficacy_SE",
                 LowerEfficacyIsBetterDrugEffect = TRUE, 
                 Efficacy_Metric_Name = "Viability",
                 Drug1 = first_drug, 
                 Drug2 = second_drug, 
                 Average_Duplicate_Records = FALSE, 
                 n_Simulations = 10000, 
                 Calculate_IDAcomboscore_And_Hazard_Ratio = TRUE, 
                 Calculate_Uncertainty = TRUE, 
                 Return_Bootstrap_Values = FALSE
                 ) 


All_IDACombo_Scores <- All_IDACombo_Scores <- temp[[1]] %>% 
  mutate(Drug1 = first_drug, Drug2 = second_drug) %>% 
  mutate(across(.cols = starts_with("p_"), 
                .fns =  function(column){as.numeric(gsub("<", "", column))}   )  ) %>% 
  bind_rows(All_IDACombo_Scores, .)

}

All_IDACombo_Scores <- All_IDACombo_Scores %>% type_convert() #for some reason, the drugXdose columns are character after this, so converting types allows to fix that

```


filtering out drugs that aren't used in any of the analyses:

The drugs in the follow-up panel that did not validate and thus were excluded from analysis were the following: Saracatinib (AZD 0530), Delanzomib (CEP-18770), IMD 0354, and MCB-613.

```{r}
unable_to_validate_drugs <- c("Saracatinib (AZD0530)", "Delanzomib (CEP-18770)", "IMD 0354", "MCB-613")

All_IDACombo_Scores <- All_IDACombo_Scores %>% 
  filter(! Drug1 %in% unable_to_validate_drugs, 
         ! Drug2 %in% unable_to_validate_drugs) %>% 
  filter(Drug1Dose != 10, 
         Drug2Dose != 10)

```


## Save results

```{r}
All_IDACombo_Scores$MaxHR <- pmax(All_IDACombo_Scores$HR_vs_Drug1,All_IDACombo_Scores$HR_vs_Drug2 )
All_IDACombo_Scores$MaxHR_pvalue <- pmax(All_IDACombo_Scores$`p_HR_vs_Drug1>=1`,All_IDACombo_Scores$`p_HR_vs_Drug2>=1` )
All_IDACombo_Scores$p_adj_IDACombo <- p.adjust(p = All_IDACombo_Scores$`p_IDA_Comboscore<=0`, method = "BH")
#write_rds(x = All_IDACombo_Scores, file = "FollowUpScreen_AllIDACombo_scores.rds")

# All_IDACombo_Scores %>%
#   readr::write_tsv(file = "IDACombo_Output_noParental.tsv")
```





